### 2020-11-03 doc/manuscript/Dow_manuscript.Rmd
separately formatted hypothesis table, inserted in manuscript

#captions
#tables
hypothesis_table_caption <-"Table 1. Hypothesis table. (NEEDS FORMATTING...obviously!)"

#figures
schematic_caption <- "Figure 1. Schematic illustrating the parameters considered here. Shown are measurements for an example tree (## cm SPECIES), fit with the model of McMahon & Parker (2015), from which phenology and growth rate parameters are obtained."

@@

# SUPPLEMENTARY INFO
#SI table numbers
sample_size_by_year= "S1"

@@

```{r hypothesis_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)  
hypothesis_table <- read.csv(file = "tables_figures/hypothesis_table.csv")
knitr::kable(hypothesis_table, caption = hypothesis_table_caption)
```

>>>>

#figure captions

schematic_caption <- "Figure 1. Schematic illustrating the parameters considered here. Shown are measurements for an example tree (## cm SPECIES), fit with the model of McMahon & Parker (2015), from which phenology and growth rate parameters are obtained."

@@

# SUPPLEMENTARY INFO (this chunk must be repeated in Dow_SI.Rmd)
#SI table numbers
sample_size_by_year= "S1"

@@

```{r hypothesis_table, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::include_graphics("tables_figures/hypothesis_table.png")
```
